\documentclass{resume} % Use the custom resume.cls style
\usepackage{fontawesome}
\usepackage[left=0.2 in,top=0.2in,right=0.2 in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%----------------------------------------------------------------------------------------
% Contact Information
%----------------------------------------------------------------------------------------


\name{Ibragim Zubailov} % Your name
\address{
    \hspace{35pt} % margin left
    \href{tel:38568458679}{\faMobile\hspace{3pt}+385 68 458679} \\
    \href{https://t.me/vulgarnykarlson}{\faPaperPlane\hspace{3pt}Telegram} \\
    \href{mailto:karlson.zim@gmail.com}{\faAt\hspace{3pt}karlson.zim@gmail.com} \\
    \href{https://linkedin.com/in/karlsondev}{\faLinkedinSquare\hspace{3pt}LinkedIn} \\
    \href{https://github.com/vulgarnykarlson}{\faGithub\hspace{3pt}Github} \\
    \href{https://gitlab.karlson.dev/individual}{\faGlobe \hspace{3pt}Portfolio} \\
    \href{https://maps.app.goo.gl/YJh4mzRDZnpb5uRo9}{\faMapMarker\hspace{3pt}Montenegro}
}
\begin{document}

%----------------------------------------------------------------------------------------
% Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{\textbf{Skills}}
       \textbf{Programming}: Go, TypeScript, Node.js, PHP, NestJS, Web3(Blockchain)
       \\ \textbf{Storage\&MQ}: Clickhouse, Postgres, MySQL, Redis, Aerospike, Kafka, RabbitMQ, NATS
       \\ \textbf{Others}: GlusterFS, ElasticSearch, Docker, Kubernetes, Ansible, Nginx, Prometheus, Grafana
       \\ \textbf{Languages}: Russian (native), English (intermediate)
\end{rSection}
%----------------------------------------------------------------------------------------
% Professional Summary
%----------------------------------------------------------------------------------------

\begin{rSection}{\textbf{Professional Summary}}
{ I am a Software engineer and leader with a 7 years of experience, with strong fundamentals in Node.js, Go, Architecture and Database
knowledge.
\\ My expertise in handling high-load systems has provided me with the knowledge to craft optimal application architecture, conduct A/B testing, and transition from monolithic to microservice systems, catering to both business requirements and overall team efficiency.
\\ I've consistently analyzed every aspect of third-party technology implementation, risk assessment, transition phases, and understanding the pros/cons derived from their usage.
}

\end{rSection}

%----------------------------------------------------------------------------------------
% Work Experience
%----------------------------------------------------------------------------------------
\begin{rSection}{\textbf{Work Experience} (6.5 years) }

\textbf{MTS Group} \hfill \textit{Moscow, Russia} \\
\textbf{Senior Go and Node.js Developer}  \hfill Jun 2022 --- Jun 2023
\begin{itemize}
    \setlength\itemsep{-0.4em}
    \item Develop high-load b2b storage.
    \item Service for optimizing load-balance of storage throughput.
    \item Optimized retrieve data from storage.
\end{itemize}
\\Stack: Go, Node.js, Kafka, Clickhouse, RabbitMQ, GlusterFS

\textbf{Lofty} \hfill \textit{Moscow, Russia} \\
\textbf{Teamlead (8 backend)} \hfill May 2020 --- May 2022
\begin{itemize}
    \setlength\itemsep{-0.4em}
    \item Developed arbitrage project between advertisers(DSP) and supply platforms (SSP). Actively participated in strategizing
    	   business logic development.
    	   After 2 years project was generating over 1mil\$ revenue, and having ~500k rps.
    \item Processes added to the team:KPI performance review, roadmap planning, mentoring, idea submission point, task decoupling.
    \item Developed traffic quality evaluation system to predict prices for SSP
    \item Developed filter system to screen out fraudulent and low-quality traffic.
\end{itemize}
\\Stack: Go, Aerospike, Kafka, Clickhouse, Postgres, GRPC

\textbf{Techlead (4 backend)} \hfill Oct 2019 --- May 2020
\begin{itemize}
    \setlength\itemsep{-0.4em}
    \item Rewrote main application to achieve: stability(no fires), 3x perfomance, A/B Business testing, unit/integration tests, low
    	    entry threshold(for newcomers).
    	    In 2y growed from 15k to 150k rps.
    \item Introduced Agile pipeline, involved in the recruitment process
    \item Participated in architecture design including devop's and database storage parts.
\end{itemize}
\\Stack: Node.js, Clickhouse, Postgres, Redis, Kafka

\textbf{Senior Node.js Developer} \hfill Jul 2019 --- Oct 2019
\begin{itemize}
    \setlength\itemsep{-0.4em}
    \item Develop high-load (70k rps) push advertisement sender, with a big flexibility of settings.
    \item Microservice for authorization
\end{itemize}
\\Stack: Node.js, MySQL, RabbitMQ

\textbf{Belsona Investment Group} \hfill \textit{Moscow, Russia} \\
\textbf{Middle Node.js Developer}  \hfill Jun 2017 --- Jul 2019

\begin{itemize}
    \setlength\itemsep{-0.4em}
    \item Develop arbitrage bot between blockchain smart-contract and exchange (Binance/Bitfinex).
    \item Design and develop risk evaluation system and a predictive model based on market trends,trading data,blockchain activities.
    \item Automation scripts for reducing routine tasks, specifically for ICO projects
    \item Devised service for risk score ICO products.
\end{itemize}
\\Stack: Node.js, MySQL, TypeScript, Web3(Ethereum), Websockets

\end{rSection}
%----------------------------------------------------------------------------------------
% Extra-curricular Activities
%----------------------------------------------------------------------------------------
%\begin{rSection}{\textbf{Extra-curricular activities} }
% leetcode, competitions, algoexpert certificate
%\end{rSection}


%----------------------------------------------------------------------------------------
% Education Section
%----------------------------------------------------------------------------------------

\begin{rSection}{\textbf{Education}}

\textbf{Bachelor's degree, Computer and Sep 2013 - May 2017 Information Systems Security} \hfill {Sep 2013 --- May 2017} \\
	  Dagestan State University

\end{rSection}

\end{document}
